Responses to Reviews

### 2016-07-12 RMS/responses.tex
almost finish 2nd revision, spell check needed

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\textbf{Jiaxiang: }}#1{ \textbf{ End}}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{\medskip\noindent\textbf{ RESPONSE: }}
\newcommand{\COMMENT}{\medskip\noindent\textbf{ COMMENT: }}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
%\title{Corrections to Manuscript No. 15-TIE-3480}
\title{Responses to Reviews}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

%% \twocolumn[
%%   \begin{@twocolumnfalse}
\maketitle

\begin{center}
  \begin{tabular}{r l}
    \hline\hline
    & \\
    Manuscript Number: & 15-TIE-3480.R1\\
    Manuscript Title: & Formal Modeling and Verification of a \\
    & Rate-Monotonic Scheduling Implementation \\
    & with Real-Time Maude \\
    Submitted to: & Transactions on Industrial Electronics \\
    Manuscript Type: & Regular paper \\
    & \\
    \hline\hline
  \end{tabular}
  \bigskip
\end{center}

@@

\section{General Response}
We thank all the reviewers for their invaluable comments, which help
us a lot in improving the paper. We believe that the paper is now more
self-contained and better presented than the original submission.

According to the comments, we make some minor revisions, which are
highlighted in the manuscript.  And detailed responses to all the
comments are shown in the rest of this document.

@@

Yes, we also agree that Theorem 2 is important. We would consider
including the detailed proof in the printed version, if the page limit
of TIE permits.

@@

{[Section II.B, page 2]} left column, lines 37-38:
What are $u_j$ and $v_j$? Are they terms too? This should be specified
in the text.

@@

{[Section II.B, page 2]} left column, lines 42-46:
I guess $s'$ is the destination state. This should be specified in the
text.  The sentence "IR and TR together..." should not be part of the
item. It should go into a new paragraph after the list.

@@

{[Section II.B, page 2]} right column, lines 22-24:
As it seems the timed operators are not used, I suggest to avoid
mentioning them. By the way, this mention without any other detail is
useless.

@@

Thanks for the suggestion. Actually some of the timed operators are
used in Section V.A when describing the properties we verify. This
little problem is addressed now. We now only mention the necessary
timed operators which will be used, and also add explanations when
using them in Section V.A.

@@

{[Page 4]} line 45: 
Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?

@@

In our model, as we discuss in Section IV.A, a \verb|Counter| contains
two elements: the execution time (the time how long a task has been
executing for) and the computation requirement (the time how long a
task should execute for). A \verb|Counter| is some kind of
``dynamic''. It is like a countdown timer to complete the execution of
a task. Different from \verb|Counter|, a period is a ``static''
property of a task. Therefore, a period is modeled as a term of sort
\verb|Nat| instead of \verb|Counter|.

On the other hand, a period can also be modeled as a \verb|Counter|.
Then it becomes a countdown timer to trigger an execution request of
the task, while the execution requests are currently triggered by the
periodic interrupts in our model.

@@

Thanks for the pros and the careful reading.

``monus'' is the name of the built-in minus operation defined in
Real-Time Maude, as we introduced in Lemma A.1 at page 8 in the
Appendix. It is not a typo. We have also spell checked the whole
manuscript again to avoid typos.

>>>>

\usepackage{alltt}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepackage{multicol}
\newcommand{\hide}[1]{\ignorespaces}
\newcommand{\jx}[1]{{\textbf{Jiaxiang: }}#1{ \textbf{ End}}}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\ANSWER}{\medskip\noindent\textbf{RESPONSE: }}
\newcommand{\COMMENT}{\medskip\noindent\textbf{COMMENT: }}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
%\title{Corrections to Manuscript No. 15-TIE-3480}
\title{Responses to Reviews}
\date{}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

%% \twocolumn[
%%   \begin{@twocolumnfalse}
\maketitle
\vspace{-30pt}
\begin{center}
  \begin{tabular}{r l}
    \hline\hline
    & \\
    Manuscript Number: & 15-TIE-3480.R1\\
    Manuscript Title: & Formal Modeling and Verification of a \\
    & Rate-Monotonic Scheduling Implementation \\
    & with Real-Time Maude \\
    Submitted to: & Transactions on Industrial Electronics \\
    Manuscript Type: & Regular paper \\
    & \\
    \hline\hline
  \end{tabular}
  \bigskip
\end{center}

@@

\section{General Response}
We thank all the reviewers for their invaluable comments, which help
us a lot in improving the paper.

%% We believe that the paper is now more
%% self-contained and better presented than the original submission.

According to the comments, we make several minor revisions, which are
highlighted in the manuscript.  And detailed responses to all the
comments are shown in the rest of this document.

@@

%% As to Theorem~2, we also agree that it is important. But due to the
%% page limit of TIE, we have to refer the detailed proof of this theorem
%% to the technical report, where the proof is more detailed and more
%% self-contained.

We agree that Theorem~2 is very important and that is also the reason
we have carefully revised the proof and extended it to contain all
necessary deduction steps. However, due to the space limit of TIE, we
found it almost impossible to include the proof without comprising
other important details of the paper. As a result, we have to put the
detailed proof as a separate technical document.

%% Yes, we also agree that Theorem 2 is important. We would consider
%% including the detailed proof in the printed version, if the page limit
%% of TIE permits.

@@

[Section II.B, page 2] left column, lines 37-38:
What are $u_j$ and $v_j$? Are they terms too? This should be specified
in the text.

@@

[Section II.B, page 2] left column, lines 42-46:
I guess $s'$ is the destination state. This should be specified in the
text.  The sentence "IR and TR together..." should not be part of the
item. It should go into a new paragraph after the list.

@@

[Section II.B, page 2] right column, lines 22-24:
As it seems the timed operators are not used, I suggest to avoid
mentioning them. By the way, this mention without any other detail is
useless.

@@

Thanks for the suggestion. It is addressed now. Actually some of the
timed operators are used in Section~V.A when describing the properties
we verify. We now only mention the necessary timed operators which
will be used, and also add explanations when using them in
Section~V.A.

@@

[Page 4] line 45: 
Why is a period of sort \verb|Nat|? Shouldn't it be \verb|Counter|?

@@

In our model, a period is of sort \verb|Nat| instead of
\verb|Counter|.
%% as we discuss in Section IV.A, a \verb|Counter| contains
%% two elements: the execution time (the time how long a task has been
%% executing for) and the computation requirement (the time how long a
%% task should execute for).
A \verb|Counter| is some kind of ``dynamic''. It is like a countdown
timer to complete the execution of a task. However, a period is a
``static'' property of a task. Therefore, a period is modeled as a
term of sort \verb|Nat| instead of \verb|Counter|.

On the other hand, a period can also be modeled as a \verb|Counter|.
Then it becomes a countdown timer to trigger an execution request of
the task.
%% while the execution requests are currently triggered by the
%% periodic interrupts in our model.

@@

Thanks for your pros and carefully reading. However, ``monus'' is not
a typo but the name of the built-in minus operation defined in
Real-Time Maude (as explained in Lemma A.1). We have done proof
checking again to avoid other typos.

%% Thanks for the pros and the careful reading. We have spell checked
%% again the whole manuscript to avoid typos.

%% ``monus'' is not a typo. It is the name of the built-in minus
%% operation defined in Real-Time Maude, as we introduced in Lemma A.1 at
%% page 8 in the Appendix.
